### 2020-03-31 manuscript/manuscript.rmd
standin for fig5 for now

```{r phylogenetic_signal, fig.width=6, fig.height=12}
fig5_bars <- au_tests %>%
  unite(Matrix, c(manuscript, matrix, model)) %>%
  group_by(Matrix, result) %>%
  count() %>%
  group_by(Matrix) %>%
  mutate(percent = prop.table(n)) %>%

@@

fig5_tbl <- au_tests %>%
select(c(manuscript, matrix, model)) %>%
distinct()

fig_5_ylabs_grob <- tableGrob(fig5_tbl)
fig_5_ylabs$heights = unit(rep(1/nrow(fig_5_ylabs), nrow(fig_5_ylabs)), "npc")
fig_5_ylabs$widths = unit.pmax(fig_5_ylabs$widths, unit(2, "lines"))

fig5_bars_grob <- ggplotGrob(fig5_bars)
#fig5 <- gtable_add_cols(fig5, sum(fig_5_ylabs$widths), pos=0)
#fig5 <- gtable_add_grob(fig5, grobs = fig_5_ylabs, t=6, l=ncol(fig5), b=6, r=ncol(fig5))
#fig5 <- gtable_add_grob(fig5, grobs = fig_5_ylabs, t=6, l=1, b=6, r=ncol(fig5))

grob_grid <- matrix(list(fig_5_ylabs_grob, fig5_bars_grob), nrow = 1)
# https://cran.r-project.org/web/packages/gridExtra/vignettes/gtable.html

>>>>

```{r phylogenetic_signal, fig.width=6, fig.height=12}
# fig5_bars <- au_tests %>%
au_tests %>%
  unite(Matrix, c(manuscript, matrix, model)) %>%
  group_by(Matrix, result) %>%
  count() %>%
  group_by(Matrix) %>%
  mutate(percent = prop.table(n)) %>%

@@

#fig5_tbl <- au_tests %>%
#select(c(manuscript, matrix, model)) %>%
#distinct()

#fig_5_ylabs_grob <- tableGrob(fig5_tbl)
#fig_5_ylabs$heights = unit(rep(1/nrow(fig_5_ylabs), nrow(fig_5_ylabs)), "npc")
#fig_5_ylabs$widths = unit.pmax(fig_5_ylabs$widths, unit(2, "lines"))

#fig5_bars_grob <- ggplotGrob(fig5_bars)
#fig5 <- gtable_add_cols(fig5, sum(fig_5_ylabs$widths), pos=0)
#fig5 <- gtable_add_grob(fig5, grobs = fig_5_ylabs, t=6, l=ncol(fig5), b=6, r=ncol(fig5))
#fig5 <- gtable_add_grob(fig5, grobs = fig_5_ylabs, t=6, l=1, b=6, r=ncol(fig5))

#grob_grid <- matrix(list(fig_5_ylabs_grob, fig5_bars_grob), nrow = 1)
# https://cran.r-project.org/web/packages/gridExtra/vignettes/gtable.html
